Open Source, Collaborative Curriculum

### 2017-04-29 siip.tex
adds note about insitutional outcomes

\usepackage[acronym,toc]{glossaries}
\include{acros}
\makeglossaries
\usepackage{fancyhdr}
\usepackage{pagecounting}
\usepackage[dvips]{color}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{placeins}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}

% Trying to bold my name in the bib
\usepackage{xstring}
\def\FormatName#1{%
          \IfSubStr{#1}{Huff}{\textbf{#1}}{#1}%
          }

@@

          Previous attempts at collaborative curriculum development have met with 
          challenges. Most notable among these is Software Carpentry (with 
          which the PI and Co-PI are quite involved) 
          \cite{wilson_software_2014}.  Software Carpentry teaches 
          computational skills for scientists using a shared curriculum hosted 
          on GitHub. Instructors can use and remix the curriculum, but our 
          experience showed that instructors improved on the original material, 
          but lacked a  strong incentive for contribution back to the master 
          material. Thus, versions of the original material tended to diverge 
          rather than converge 
          \cite{wilson_software_2014,wilson_software_2014-1}.

@@

          The participants will collaborate on a master set of learning 
          modules for an upper-division course in nuclear engineering : 
          on The Nuclear Fuel Cycle. In the near term, we will develop 
          fine-grained lessons and assessments which may be mixed and matched 
          to meet the learning objectives. The curriculum will be hosted on 
          GitHub, tested by all of us, and improved continually.

          Prof. Neal Davis, Co-PI of this proposal, has contemplated a 
          Collaborative Computational Curriculum for some time 
          \cite{davis_ui-ccc_2016}. Since he 
          teaches large-scale 
          computational curriculum at UIUC 
          he is an ideal person to potentially scale-up this work in the 
          future. Additionally, he has the nuclear engineering background to 
          understand the context of this prototyping effort. Prof. Davis' role 
          in this effort will be to conduct \emph{action research}, observing 
          our process and teasing out potential avenues for future 
          extensions and applications of the process.

@@

          \paragraph{UIUC Institutional Outcomes}

          Fame, glory.

@@

          \begin{itemize}
                  \item[Jul 2017] 1st Workshop
                  \item[Aug 2017 - Jun 2018] Monthly Video Conferences 
                  \item[Jul 2018] Retrospective Workshop
          \end{itemize}

>>>>

\usepackage[acronym,toc]{glossaries}
\include{acros}
\makeglossaries
\usepackage{fancyhdr}
\usepackage{pagecounting}
\usepackage[dvips]{color}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{placeins}
%\usepackage{chronology}
\usepackage{tabularx}
\usepackage[hidelinks]{hyperref}

% Trying to bold PI names in the bib
\usepackage{xstring}
\def\FormatName#1{%
          \IfSubStr{#1}{Huff}{\textbf{#1}}{\IfSubStr{#1}{Neal Davis}{\textbf{#1}}{#1}}%
          }

@@

          Previous attempts at collaborative curriculum development have met with 
          challenges. Most notable among these is Software Carpentry (with 
          which the PI and Co-PI are quite involved) 
          \cite{wilson_software_2014}.  Software Carpentry teaches 
          computational skills for scientists using a shared curriculum hosted 
          on GitHub. Hundreds of instructors accross the planet use and remix 
          the curriculum, but our experience showed that while these 
          instructors used and improved on the original material, they rarely 
          contributed their changes back to the master material. Thus, versions 
          of the original material tend to diverge rather than converge 
          \cite{wilson_software_2014,wilson_software_2014-1}.

@@

          The participants will collaborate on a master set of learning 
          modules for an upper-division course in nuclear engineering : 
          The Nuclear Fuel Cycle. In the near term, we will develop 
          fine-grained lessons and assessments which may be mixed and matched 
          to meet the learning objectives. The curriculum will be hosted on 
          GitHub, tested by all of us, and improved continually.

          Prof. Neal Davis, Co-PI of this proposal, has contemplated a 
          Collaborative Computational Curriculum for some time 
          \cite{davis_university_2016}. Since he 
          teaches large-scale 
          computational curriculum at UIUC 
          he is an ideal person to potentially scale-up this work in the 
          future. Additionally, he has the nuclear engineering background to 
          understand the context of this prototyping effort. Prof. Davis' role 
          in this effort will be to conduct \emph{action research}, observing 
          our process and teasing out potential avenues for future 
          extensions and applications of the process.

@@

          \paragraph{UIUC Institutional Outcomes} Openness and collaboration 
          both increase visibility. The leadership of UIUC College of 
          Engineering faculty in this effort, if successful, will be exemplary 
          of the forward-thinking nature of the college and the university at 
          large. Furthermore, extensions to this work may be competitive for  
          support from educational grant-making agencies such as the National 
          Science Foundation and even private foundations such as Moore and 
          Sloan.

@@

          %\input{timeline}
          \begin{itemize}
                  \item[Jul 2017] 1st Workshop
                  \item[Aug 2017 - Jun 2018] Monthly Video Conferences 
                  \item[Jul 2018] Retrospective Workshop
          \end{itemize}
